A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-02 mt-marathon.2013/PBML_article.tex
script to replace numbers with placeholder. /Achim Ruopp

\section{Hypothesis and Translation Rule Evaluation}
\subsection{Old Framework}
The range of feature functions were hardcoded when evaluating the scores of hypotheses and translation rules. Translation rules are evaluated according to Equation~\ref{eq:translation rule score}
\begin{equation}
  score = \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) + \sum_{l  \in L} (\lambda_l * score_i) + \lambda_{wp} * words
\label{eq:translation rule score}
\end{equation}
where $T$ is the set of translation models, and $L$ is the set of sequence models, $\lambda_{m,i}$ is the i'th weight for translation model $m$, $\lambda_l$ is the weight for language model $l$, $\lambda_{wp}$ is the word penalty weight.

Similarly, hypotheses are evaluated as follows, Equation~\ref{eq:hypothesis rule score}:
\begin{equation}
\begin{split}
 score & =  \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) \\
    & + \sum_{l \in L} (\lambda_l * score_l) \\
    & + \lambda_{wp} * words \\
    & + \lambda_d * score_d \\
    & + \sum_{m \in R} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) %\\
%    & + score_{future} \\
\label{eq:hypothesis rule score}
\end{split}
\end{equation}
where $\lambda_d$ is the distortion weight, and $R$ is the set of lexicalized reordering models.
%, and $score_{future}$ is the estimate of the future score for the hypothesis.

@@

Translation rule always evaluated occurs before decoding, either during loading of the feature function, or just before the translation rule is used in decoding.

Hypotheses are evaluated when they are created during the search process.

@@

Equation (1) becomes Equation (...)
\begin{equation}
  score = \sum_{i \in FF}(\lambda_i * score_i)
\end{equation}
where $FF$ is the set of feature functions.

Equation (2) becomes Equation (...)
\begin{equation}
  score =  \sum_{i \in FF}(\lambda_i * score_i)
	  + score_{future}
\end{equation}

Furthermore, there are three places where each feature function can be evaluated. At each place, a different range of information is available to the feature function to access for information.

    1. During creation of translation rules. Access to the words in the source and target side of translation rule.

    2. Just before decoding. Access to the entire source sentence to be decoded.

    3. During decoding. Access to the context information is available, containing the hypotheses create to translate the sentence so far. The exact information contained in the hypotheses is dependent on whether the formalism used.

Scores that are evaluated at stage one can be cached and reused inter-sentence. Scores evaluted during stage (2) and (3) cannot be cached as they depend on the entire source sentence. Therefore, it is more efficient to evaluate as early as possible.

Each feature function can override any or all of the method to evaluate at each of these stage. For example. a simple word penalty feature would typically implement its evaluation in stage (1) as access to the translation rule is sufficient information to allow it to evaluate the word penalty score.

@@

Stateful features, and features that depend on the segmentation of the input sentence, need to override stage (3).

@@

\subsection{CDEC and Joshua}
Moses implements a one-pass search strategy. All feature functions are evaluated when a hypothesis is created.

Joshua and CDEC employs a multi-pass search strategy to translate each sentence. Each pass creates a hypergraph that is used as the input for the next pass. Both decoders evaluates stateless feature functions in the first pass, then stateful feature functions in the second.

CDEC also supports an arbitary number of passes and split the feature functions between those passes.

>>>>

\section{Hypothesis and Translation Rule Evaluation}
\subsection{Old Framework}
The range of feature functions are hardcoded when evaluating the scores of hypotheses and translation rules. Translation rules are evaluated according to Equation~\ref{eq:translation rule score}:
\begin{equation}
  score = \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) + \sum_{l  \in L} (\lambda_l * score_i) + \lambda_{wp} * words
\label{eq:translation rule score}
\end{equation}
where $T$ is the set of translation models, and $L$ is the set of sequence models, $\lambda_{m,i}$ is the i'th weight for translation model $m$, $\lambda_l$ is the weight for language model $l$, $\lambda_{wp}$ is the word penalty weight.

Similarly, hypotheses are evaluated as follows, Equation~\ref{eq:hypothesis rule score}:
\begin{equation}
\begin{split}
 score & =  \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) \\
    & + \sum_{l \in L} (\lambda_l * score_l) \\
    & + \lambda_{wp} * words \\
    & + \lambda_d * score_d \\
    & + \sum_{m \in R} \sum_{i \in m} (\lambda_{m,i} * score_{m,i})  \\
    & + score_{future} \\
\label{eq:hypothesis rule score}
\end{split}
\end{equation}
where $\lambda_d$ is the distortion weight, and $R$ is the set of lexicalized reordering models, and $score_{future}$ is the estimate of the score to completion for the hypothesis.

@@

%Translation rule always evaluated occurs before decoding, either during loading of the feature function, or just before the translation rule is used in decoding.

%Hypotheses are evaluated when they are created during the search process.

@@

Equation~\ref{eq:translation rule score} becomes Equation~\ref{eq:translation rule score.new}
\begin{equation}
  score = \sum_{m \in FF} \sum_{i \in m} (\lambda_{m,i} * score_{m,i})
\label{eq:translation rule score.new}
\end{equation}
where $FF$ is the set of feature functions.

Similarly, Equation~\ref{eq:hypothesis rule score} becomes Equation~\ref{eq:hypothesis rule score.new}:
\begin{equation}
  score =  \sum_{m \in FF} \sum_{i \in m} (\lambda_{m,i} * score_{m,i})
	  + score_{future}
\label{eq:hypothesis rule score.new}
\end{equation}

Furthermore, there are three stages during decoding where each feature function can be evaluated:
\begin{enumerate}
    \item During creation of translation rules. Access to the words in the source and target side of translation rule.
    \item Just before decoding. Access to the entire source sentence to be decoded.
    \item During decoding. Access to the context information is available, containing the hypotheses create to translate the sentence so far. The exact information contained in the hypotheses is dependent on whether the formalism used.
\end{enumerate}
At each stage, a different range of information is available to the feature function to access for information. Scores that are evaluated at stage (1) can be cached and reused inter-sentence. Scores evaluted during stage (2) and (3) cannot be cached as they depend on the entire source sentence. Therefore, it is more efficient to evaluate as early as possible.

Each feature function can override any or all of the methods to evaluate at each of these stage. For example. a simple word penalty feature would typically implement its evaluation in stage (1) as access to the translation rule is sufficient information to allow it to evaluate the word penalty score.

@@

Stateful features need to override stage (3). Features that depend on the segmentation of the input sentence also need to override this stage.

@@

\subsection{cdec and Joshua}
Moses implements a one-pass search strategy. All feature functions are evaluated when a hypothesis is created.

Joshua and cdec employs a multi-pass search strategy to translate each sentence. Each pass creates a hypergraph that is used as the input for the next pass. Both decoders evaluates stateless feature functions in the first pass, then stateful feature functions in the second.

cdec also supports an arbitrary number of passes, feature functions exactly to a particular pass.
